Supplementary material: When does vapor pressure deficit drive or reduce evapotranspiration?

### 2019-09-03 doc/paper/agu-james-original-submission.tex
seems easier to use latexdiff than agu's recommendation of trackchanges

\begin{keypoints}
\item Using Penman-Monteith, a semi-empirical stomatal conductance
  model, and underlying water use efficiency, we develop a simplified
  analytical theory for when ecosystems will reduce or increase
  evapotranspiration in response to increasing vapor pressure deficit.
\item Variations in ecosystem characteristics and environmental
  conditions result in a broad range of responses to increases in
  vapor pressure deficit, from strong reductions to strong increases
  in evapotranspiration.
\item The choice of stomatal conductance model fundamentally alters
  the relationship between evapotranspiration and vapor pressure
  deficit, highlighting the need for further research on stomatal
  conductance and its representation in more sophisticated land
  surface models.
\end{keypoints}

>>>>

\begin{keypoints}
\item We derive a simplified analytical model for ecosystem-scale
  evapotranspiration response to changes in vapor pressure deficit.
\item Ecosystems exhibit a range of behavior, from reductions to
  increases in evapotransipration, in response to increasing vapor
  pressure deficit.
\item The choice of stomatal conductance model fundamentally alters
  the relationship between evapotranspiration and vapor pressure
  deficit.
\end{keypoints}

### 2019-09-03 doc/paper/james-supplement-original-submision.tex
seems easier to use latexdiff than agu's recommendation of trackchanges

The paper does not rely on assumptions about uWUE's functional
relationship with soil moisture so we do not include the figures in
the body of the manuscript. But given that constant uWUE g$_1$
assumptions can make our theory more useful to the reader we provide
the figures for their interpretation, and motivation for future
research.

>>>>

The paper does not rely on assumptions about uWUE's functional
relationship with soil moisture so we do not include the figures in
the body of the manuscript. But given that constant uWUE and g$_1$
assumptions can make our theory more useful to the reader we provide
the figures for their interpretation, and motivation for future
research.
